Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-01 paper/paper.qmd
update paper

```{r}
#| include: false
#| warning: false
#| message: false
harris_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data_Harris.parquet"))
trump_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data_Trump.parquet"))
```

@@

## Model{#forth-model}

We conducted a regression analysis to predict support for Kamala Harris
and Donald Trump in the 2024 U.S. presidential election, including
models for Trump for comparison. Our analysis includes four models:
**unweighted linear models** and **weighted linear models** for both
candidates. These models predict each candidate’s support as a
continuous outcome across different states, using **pollster**,
**national poll**, and **population** as key predictors. The weighted
models additionally incorporate adjustments for recency, sample size,
and poll quality to account for potential biases. This setup aligns with
the New York Times methodology for election polling, which assigns
weights based on poll quality, sample size, and recency to better
reflect voter sentiment [@nyt_polling_averages].

The validation and diagnostic details of the model are provided in
[Appendix B](#sec-model-details)

## Model Set-up

We implemented our linear regression models using the `lm()` function in
R.

### Mathematical Expressions

Both the unweighted and weighted models share the same mathematical
expression format:

```{r}
#| include: false
#| warning: false
#| message: false
harris_unweighted_model <- readRDS(here::here("models", "model_harris_unweighted.rds"))
harris_weighted_model <- readRDS(here::here("models", "model_harris_weighted.rds"))
trump_unweighted_model <- readRDS(here::here("models", "model_trump_unweighted.rds"))
trump_weighted_model <- readRDS(here::here("models", "model_trump_weighted.rds"))
```

@@

The unweighted model for Harris provides a baseline by treating all
polls equally without adjustments for recency, sample size, or poll
quality:

$$
\text{Support\_Harris}_i = \beta_0 + \beta_1 \cdot \text{National\_Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
$$

#### Weighted Model

The weighted model for Harris incorporates adjustments for recency,
sample size, and pollster quality:

$$
\text{Support\_Harris}_i = \beta_0 + \beta_1 \cdot \text{National\_Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
$$

```{r}
#| include: false
#| warning: false
#| message: false
#### Calculate Weights ####
# Calculate weights for Harris data
harris_data <- harris_data |>
  mutate(
    sample_size_weight = pmin(sample_size / 2300, 1),
    pollster_quality_weight = numeric_grade / 4,
    recency_weight = exp(-recency * 0.1)
  ) |>
  group_by(pollster) |>
  mutate(
    recent_poll_count = sum(recency < 30),
    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
  ) |>
  ungroup() |>
  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)

# Calculate weights for Trump data
trump_data <- trump_data |>
  mutate(
    sample_size_weight = pmin(sample_size / 2300, 1),
    pollster_quality_weight = numeric_grade / 4,
    recency_weight = exp(-recency * 0.1)
  ) |>
  group_by(pollster) |>
  mutate(
    recent_poll_count = sum(recency < 30),
    poll_frequency_weight = ifelse(recent_poll_count > 4, 4 / recent_poll_count, 1)
  ) |>
  ungroup() |>
  mutate(combined_weight = recency_weight * sample_size_weight * poll_frequency_weight * pollster_quality_weight)
```

### Coefficient Explanations

-   $\beta_0$: Intercept of the model, representing the expected support
    when all predictors are zero.
-   $\beta_1$: Coefficient for the national poll, indicating how much
    support changes with a one-unit increase in the national poll
    percentage.
-   $\beta_2$: Coefficient for the pollster, reflecting the impact of
    different polling organizations on support.
-   $\beta_3$: Coefficient for the population, accounting for the
    influence of the demographic context on support levels.

### Model Justification

1.  **Weighted Least Squares Estimation**

In our analysis, we utilize weighted least squares estimation to account
for the varying quality of polling data. The weights are crucial in the
estimation process, leading to the following expression for the
estimates of the coefficients ($\hat{\beta}$):

@@

Where: - $X$ is the design matrix of predictors. - $W$ is the diagonal
matrix of weights, which incorporates factors such as recency, sample
size, and pollster quality to enhance the reliability of our estimates.

The weighted model is essential for accurately reflecting voter
sentiment. By incorporating weights, we adjust for the reliability of
the polling data, ensuring that more credible polls have a greater
influence on the estimates.

2.  **Calculation of Variables**:

    -   **Combined Weight**: The combined weight is calculated as
        follows: $$
        \text{combined\_weight} = \text{recency\_weight} \times \text{sample\_size\_weight} \times \text{poll\_frequency\_weight} \times \text{pollster\_quality\_weight}
        $$

    -   **Recency Weight**: This weight uses an exponential decay
        function: $$
        \text{recency\_weight} = \exp(-\text{Recency}_i \cdot 0.1)
        $$ This reflects the diminishing influence of older polls, with
        $\lambda = 0.1$ for the exponential decay.

    -   **Sample Size Weight**: This weight adjusts the significance of
        each poll based on the number of respondents, capping the
        weights at a maximum of 2,300 responses to reflect the
        reliability of larger sample sizes [@nyt_polling_averages].

    -   **Poll Frequency Weight**: This weight considers how often a
        pollster conducts polls, with higher weights assigned to
        pollsters with a greater number of recent surveys.

    -   **Pollster Quality Weight**: Based on the historical performance
        of the pollster, this weight emphasizes the reliability of their
        polling methods.

### Alternative Models

While this analysis employs linear regression with weighted least
squares, alternative methods such as Bayesian modeling could provide
additional insights. However, we opted for the weighted linear a
regression approach to maintain interpretability and ease of
implementation given the scope and resources of this analysis. The
Bayesian approach was not chosen primarily due to the complexity
involved in defining priors and the additional computational
requirements.

### Importance of Combined Weights

By incorporating these combined weights, the weighted model offers a
more nuanced estimation of voter support for both Harris and Trump.
While the mathematical expression for the models remains consistent, the
weighted models effectively adjust for variations in data quality and
recency, leading to more accurate predictions of voter sentiment.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
set.seed(233)

new_data_harris <- data.frame(
  end_date = seq(
    min(harris_data$end_date),
    max(harris_data$end_date),
    length.out = 2000
  ),
  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$pollster)), 
  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$population)),
  sample_size = sample(1:2300, size = 2000, replace = TRUE)
)|>
  mutate(
    national_poll = if_else(state == "National", 1, 0),
    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight,
    candidate="Harris"
  )

@@

# Plotting with the filtered data
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```
## Predicted Voting Outcomes for Recent Three Months by Respondent Group

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Fitted Linear Model"
#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
#| layout-ncol: 2
#| label: fig-support-respondent
custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
### unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
### weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```
## Predicted Voting Outcomes for Recent Three Months by State

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
#| layout-ncol: 2
#| label: fig-support-respondent
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

```{r}
# Load necessary package
library(knitr)
library(kableExtra)

# Example: Assume `predicted_results` is your data frame
# Ensure column names match this format
# Example structure:
# predicted_results <- data.frame(
#   State = c("Arizona", "California", ...),
#   Trump_Predicted_Percentage = c(48.94, 33.80, ...),
#   Electoral_Votes = c(11, 55, ...),
#   Winner = c("Harris", "Harris", ...)
# )

# Rename columns to match the desired table format
colnames(predicted_results) <- c("State", "Harris Predicted %", "Vote Share", "Winner")

# Generate table
predicted_results %>%
  kbl(caption = "Prediction Vote share for Trump and Harris", format = "html") %>%
  kable_styling(full_width = FALSE, position = "center") %>%
  column_spec(2, width = "5em") %>%
  column_spec(3, width = "5em") %>%
  column_spec(4, width = "5em") %>%
  add_header_above(c(" " = 1, "Trump Predicted %" = 1, "Electoral Votes" = 1, "Winner" = 1))

@@

@@

$\text{Sampling Proportion_A}$ =
$\frac{500,000}{1,200,000} \approx0.417$

@@

$\text{Sampling Proportion_B}$ =
$\frac{700,000}{1,200,000} \approx0.583$

@@

\$ \text{Polls for State A} = 1,000 \times 0.417 \approx 417\$

@@

$\text{Polls for State B} = 1,000 \times 0.583 \approx 583$

@@

10. **What do you think is the most important issue facing the United
    States?** [Select at most 3]

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
harris_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data_Harris.parquet"))
trump_data <- read_parquet(here::here("data", "02-analysis_data", "analysis_data_Trump.parquet"))
####### Model ######
harris_unweighted_model <- readRDS(here::here("models", "model_harris_unweighted.rds"))
harris_weighted_model <- readRDS(here::here("models", "model_harris_weighted.rds"))
trump_unweighted_model <- readRDS(here::here("models", "model_trump_unweighted.rds"))
trump_weighted_model <- readRDS(here::here("models", "model_trump_weighted.rds"))
```

```{r}
#| include: false
#| warning: false
#| message: false
trump_data<-trump_data |>mutate(candidate="Trump")
harris_data<-harris_data|>mutate(candidat="Harris")
combined_data_total<-bind_rows(harris_data,trump_data)
combined_data_total<-combined_data_total|>
  mutate(
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight
  ) 
```

@@

## Model {#forth-model}

Our modeling approach aims to quantify the relationship between various
polling metrics and the percentage of support for each candidate, Kamala
Harris and Donald Trump. For this analysis, we employ a linear model
(LM) to examine how factors such as national polling trends, poll
quality scores, and population size influence support percentages. The
model is implemented using the `lm` function in R, with a Gaussian
distribution to capture the variability in support rates.

In this analysis, we use predictors that capture both the methodological
quality and structural aspects of each poll. Specifically, we include
variables such as `national_poll`, which reflects national support
trends; `pollster`, which represents differences in methodology and
reliability across polling organizations; and `population`, which
accounts for demographic and regional characteristics associated with
each poll. Our combined weighting approach further integrates factors
like recency and sample size to ensure that more recent, larger-sample
polls have a greater impact on the model's predictions, providing a
balanced and comprehensive assessment of candidate support.

The model assumes that the distribution of support percentage, given
these polling characteristics, follows a normal distribution. This
Gaussian assumption enables effective parameter estimation, a standard
approach in linear regression. By applying moderate priors, we balance
interpretability with the model’s stability, allowing us to assess the
impact of polling characteristics on candidate support with greater
reliability.

### 3.1 Model Set-Up

The model predicts Harris's support percentage using the following
predictor variables:

-   **National Poll (`national_poll`)**: Represents the national trend
    in support for the candidate.
-   **Pollster (`pollster`)**: Categorical variable identifying the
    organization conducting the poll, accounting for differences in
    methodology and reliability.
-   **Population (`population`)**: Reflects demographic or regional
    characteristics associated with each poll.

@@

The unweighted model for Harris provides a baseline by treating all
polls equally without adjustments for recency, sample size, or poll
quality: The model takes the form:

$$
y_i | \mu_i, \sigma \sim \text{Normal}(\mu_i, \sigma)
$$ $$
\mu_i = \beta_0 + \beta_1 \cdot \text{National Poll}_i + \beta_2 \cdot \text{Pollster}_i + \beta_3 \cdot \text{Population}_i + \epsilon_i
$$ $$
\epsilon_i \sim \text{Normal}(0, \sigma^2)$$ Where:

-   $\beta_0$ is the intercept term, representing the baseline level of
    support.
-   $\beta_1, \beta_2, \beta_3$ are the coefficients for each predictor,
    indicating their influence on Harris's support percentage.
-   $\sigma^2$ is the variance of the error term, representing
    unobserved variability in support.

The model is executed in R, using the `lm` function for a linear
regression model. We apply weights based on `combined_weight` to account
for the importance of each poll, incorporating factors such as recency
and sample size. This approach helps ensure that more recent and
reliable polls have a greater influence on the model’s predictions.

### 3.1.1 Weighted Model Explanation

Our model uses a weighted approach to estimate candidate support more
accurately by emphasizing higher-quality and more recent polls. The
weighting scheme integrates factors like poll recency, sample size,
pollster quality, and frequency, as inspired by the New York Times’
methodology [@nyt_polling_averages] for polling averages.

In this model, weights are applied directly to each poll’s contribution
in the **Weighted Least Squares (WLS)** estimation process, modifying
the influence of each poll on the outcome. This results in the following
expression for the estimated coefficients ($\hat{\beta}$):

@@

Where:

- **Sample Size Weight**: Calculated as the sample size divided by 2300, capped at 1. This emphasizes larger, more reliable polls while preventing extremely large samples from disproportionately impacting the analysis.

- **Recency Weight**: Applied through an exponential decay function, `exp(-recency * 0.1)`, where "recency" represents the days since the poll was conducted. This ensures that more recent data carries more weight, while older polls have reduced influence.

- **Combined Weight**: The final weight is the product of all individual weights: $$
\text{Combined Weight} =\text{Recency Weight} \times \text{Sample Size Weight}
$$. This comprehensive weight prioritizes recent, large-sample, high-quality, and moderately frequent polls, creating a balanced and reliable dataset that reflects both current sentiment and credible data sources.

The **combined weight** for each poll is thus:

By incorporating these weights, we adjust the model’s estimates to give
more importance to recent, credible, and representative polls, enhancing
the reliability of our predictions.

### 3.1.2 Model Justification

Existing research and political science theories suggest that factors
such as sample size, recency, pollster reliability, and local
demographics can significantly impact support percentages for candidates
like Harris and Trump. Larger sample sizes are generally more reliable,
while recent polls capture the latest shifts in public opinion. The
methodology and timing of each poll also play a role: for instance,
online surveys and telephone interviews may capture different segments
of the population, and polling conducted during or near key political
events often reflects more immediate public sentiment. Additionally,
regional factors, such as local political dynamics or demographic
characteristics, can influence support patterns.

Our model incorporates a combined weighting scheme inspired by the
methodology outlined by the New York Times in their election polling
averages. This weighting system integrates factors like recency and
sample size, ensuring that more recent and larger-sample polls exert a
greater influence on our model's predictions. By applying this weighting
approach, we aim to achieve a balanced and representative dataset that
reflects up-to-date trends while mitigating potential biases from older
or smaller-sample polls.

A linear regression model was chosen to predict support percentages
because the dependent variable is continuous and tends to approximate a
normal distribution. Linear regression is an accessible and
interpretable method for assessing how multiple factors contribute to an
outcome, with each coefficient offering a straightforward interpretation
of predictor influence. This model framework allows us to quantify the
effects of various polling characteristics on candidate support.

Further justification for using this model stems from its alignment with
the central limit theorem, which indicates that, given a sufficiently
large sample, the distribution of support percentages should approximate
normality. Moreover, the relationships between predictors like sample
size and recency align with established theories in political behavior,
providing a theoretical basis for the model. The linear regression
approach also reduces the risk of overfitting, enhancing the
generalizability of our results to a wider set of polling data.

Finally, to ensure the robustness and accuracy of our model, we conduct
model validation and diagnostics, which are detailed in Appendix B.
These procedures help confirm that the model assumptions are met and
that the predictions are reliable across different polling scenarios.

@@

## Recent Three Months Support Trends Linear Model Prediction

```{r}
#| echo: false
#| warning: false
#| message: false
#| include: false
####### Prediction and Plot ######
set.seed(233)
####### Prediction for Harris ######
new_data_harris <- data.frame(
  end_date = seq(
    min(harris_data$end_date),
    max(harris_data$end_date),
    length.out = 2000
  ),
  state = factor(sample( c("National","Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin"), size = 2000, replace = TRUE)), 
  pollster = factor(sample(levels(harris_data$pollster), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$pollster)), 
  population = factor(sample(levels(harris_data$population), size = 2000, replace = TRUE), 
                    levels = levels(harris_data$population)),
  sample_size = sample(1:2300, size = 2000, replace = TRUE)
)|>
  mutate(
    national_poll = if_else(state == "National", 1, 0),
    recency = as.numeric(difftime(as.Date("2024-11-05"), end_date, units = "days")),
    sample_size_weight = pmin(sample_size / 2300, 1),
    recency_weight = exp(-recency * 0.1),
    combined_weight = recency_weight * sample_size_weight,
    candidate="Harris"
  )

@@

# Plotting with the filtered data
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump in 2024 US Election \n(From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))
```

## Predicted Voting Outcomes for Recent Three Months by Respondent Group

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by respondent group using Fitted Linear Model"
#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
#| layout-ncol: 2
#| label: fig-support-respondent
custom_labels <- c("lv" = "Likely Voters", "rv" = "Registered Voters")
### unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
### weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ population,ncol = 2, labeller = labeller(population = custom_labels)) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by respondent group \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

## Predicted Voting Outcomes for Recent Three Months by State

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Predicted Support Trends for Kamala Harris and Donald Trump by State using Fitted Linear Model"
#| fig-subcap: ["Predicted Support by Unweighetd Model","Predicted Support by Weighetd Model"]
#| layout-ncol: 2
#| label: fig-support-state
## unweighted
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using unweighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.7,color="grey")+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 1)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(title = "Predicted Support for Kamala Harris and Donald Trump by State \n in 2024 US Election (From August 1, 2024 to October 27, 2024)",
       subtitle = "predicted using weighted multiple linear regression model ",
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Linear Regression Model: Candidate Support Percentage =national_poll + pollster + population") +
  scale_color_manual(values = c("Harris" = "blue", "Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

@fig-national-support-trendsillustrates illustrates the polling support
trends for Kamala Harris and Donald Trump across the country from August
to October. The scatter points represent individual poll results, with
blue for Harris and red for Trump, while each dot's size reflects the
weight of the poll, accounting for factors like sample size, quality,
and recency. Harris’s support trend line generally remains above
Trump’s, with an average support level around 49%, compared to Trump’s
approximate average of 47% over this period. Toward the end of October,
both candidates show a slight increase, with Harris’s support reaching
just over 50% and Trump’s approaching 49%. This trend suggests a
potential narrowing in support levels as the election approaches,
providing a quantitative snapshot of national polling dynamics.

@@

Sampling Proportion A = $\frac{500,000}{1,200,000} \approx0.417$

@@

Sampling Proportion B = $\frac{700,000}{1,200,000} \approx0.583$

@@

Polls for State A = $1,000 {\times} 0.417 {\approx} 417$

@@

Polls for State B  = $1,000{\times} 0.583{\approx} 583$

@@

10. **What do you think is the most important issue facing the United
    States?** \[Select at most 3\]
